%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}


% job listing environments
\newenvironment{jobshort}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    }
    {
    }

\newenvironment{joblong}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
    }
    {
    \end{itemize}
    \end{minipage}    
    }



%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Ding Nan} \\[7.5pt]
\href{mailto:nandingb@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ nandingb@gmail.com} \ $|$ \ 
\href{tel:+4379888980}{\raisebox{-0.05\height}\faMobile \ 437.988.8980} \ $|$ \ 
\href{https://github.com/dingnan}{\raisebox{-0.05\height}\faGithub\ dingnan} \ $|$ \ 
\href{https://www.linkedin.com/in/dingnan/}{\raisebox{-0.05\height}\faLinkedin\ dingnan} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Interests/ Keywords/ Summary
\section{Summary}
\textbf{Senior Software Developer} with over 20 years of successful experience in enterprise software development. Brings over 5 years of hands-on experience with modern JavaScript frameworks and .NET Framework with SQL Server. A clean coder who adheres to SOLID principles and emphasizes maintainable, high-quality code.


%Experience
\section{Work Experience}

\begin{joblong}{Senior Front-End Developer, Rogers}{Aug 2022 - present}
\item Designed and implemented streaming service web pages, contributing to a significant increase in sales.
\item Implemented pagination and lazy loading on the channels page, optimizing page performance and enhancing user interaction.
\item Technologies used:  Angular 16, RxJS, NgRx, Node.js
\end{joblong}

\begin{joblong}{Senior Front-End Developer, The Home Depot}{Feb 2021 - Aug 2022}
\item Enhanced the product page by adding the Home Depot label credit card promotion feature, driving increased customer engagement and conversion rates.
\item Integrated a charity donation feature on the checkout page, boosting customer participation in charitable contributions and enhancing the brand's social impact. 
\item Implemented a sponsored products feature, generating additional revenue streams and increasing product visibility on the platform.
\item Technologies used:  Angular 10, RxJS, NgRx
\end{joblong}

\begin{joblong}{Senior Front-End Developer, BMO Bank}{Jul 2020 - Feb 2021}
\item Designed and implemented an Angular library and a showcase page for internal framework.
\item Collaborated with product team members to implement new feature.
\item Increased test coverage using Jest
\end{joblong}

\begin{joblong}{Senior Front-End Developer, Ceridian}{Oct 2019 - May 2020}
\item Migrated a large Silverlight web application to HTML5.
\item Improved web accessibility using latest accessibility standards and principles. 
\item Technologies used in this project are as follows:  Dojo Toolkit, JavaScript, HTML5, CSS3
\end{joblong}

\begin{joblong}{Senior Angular Developer, Adesa Global}{Apr 2019 - Sep 2019}
\item Worked with designers, backend developers and product owners to build a world class online used car auction platform.
\item Implemented type ahead search component using RxJS operators. 
\item Wrote all synchronous / asynchronous unit tests leveraging Karma/Jasmine.
\item Created microservices using AWS lambda functions.
\item Technologies used in this project are as follows:  Angular 7, RxJS, Node.js, AWS (Lambda, DynamoDB)
\end{joblong}

\begin{joblong}{Senior Angular Developer, TD Bank}{Oct 2018 - Mar 2019}
\item Integrated existing risk management application with third party risk rating agencies.
\item Improved risk management application with latest web technologies.
\item Technologies used in this project are as follows:  Angular 5, CSharp, TypeScript
\end{joblong}

\begin{joblong}{Senior Angular Developer, CPP Investment Board}{Feb 2018 - Sep 2018}
\item Design, develop and maintain a new product for Total Portfolio Management application.
\item Design and develop restful API endpoints using Python. 
\item Technologies used in this project are as follows:  AngularJS v1.7, TypeScript, ES6, Bootstrap, Python, SQL Server
\end{joblong}

\begin{joblong}{Senior Angular Developer, Capco}{Jun 2017 - Dec 2017}
\item Designed and developed PC financial credit card website 
\item Created restful mock backend API services. 
\item Technologies used in this project are as follows:  Angular 4, TypeScript, ES6, RxJS, Google Material Design, Flexbox, Node.js
\end{joblong}

\begin{joblong}{Senior Software Developer, Bankrate}{Jul 2012 - Feb 2017}
\item Migrated mortgage rate service from WCF to Web API.
\item Created prove of concept page using Vue.js and Angular2. 
\item Generated web page performance report using Google Page Speed service, reduced HTTP Requests and improved page load time by half.
\item Technologies used in this project are as follows:  ASP.NET Web API 2.0, CSharp, LINQ, SQL Server, Knockout JS
\end{joblong}

\begin{joblong}{Senior Software Developer, DealerTrack Canada}{Jan 2007 - Jun 2012}
\item Developed dealership finance and insurance software for the auto industry.
\item Technologies used in this project are as follows:  ASP.NET, MVC 3.0, jQuery, JavaScript, CSharp, LINQ, PL SQL, Oracle 11g
\end{joblong}

\begin{joblong}{Senior Software Developer, TD Bank}{May 2004 - Oct 2006}
\item Designed and implemented a Basel II risk management application. It helped senior lending manager to monitor and assess credit risk of large corporate loans.
\item Designed and developed an XMLHttpRequest Engine to improve credit application status page navigation speed by an average of five times with one fifth the bandwidth overhead. 
\item Designed and developed GUI for applications and modules.
\item Technologies used in this project are as follows:  ASP.NET, JavaScript, Microsoft InfoPath, SharePoint, CSharp, SQL Server
\end{joblong}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}	
1988 - 1992 & Bachelor of Computer Science at \textbf{University of Inner Mongolia - China} 
\end{tabularx}

%----------------------------------------------------------------------------------------
%	Certifications
%----------------------------------------------------------------------------------------
\section{Certifications}
\begin{tabularx}{\linewidth}{@{}l X@{}}
2019 & AWS Certified Solutions Architect - Associate\\
2004 & Microsoft Certified Solutions Developer (MCSD.NET) 
\end{tabularx}


\vfill
\center{\footnotesize Last updated: \today}

\end{document}